### 2020-04-22 readme.Rmd
update readme
update  markdown format.

---
output:
  md_document:
    variant: markdown_github
---

@@

## qrbp is an r package for generating quasi random background points for Poisson point process models.

The package aims to setup a model matrix for point process modelling of single or mulitple (marked) point processes. The package is based on the quadrature scheme proposed by Berman & Turner 1993, and Warton & Shepard 2010. The idea bebind this package is simple, provided a set of presences for a species (or multiple species) and a spatial region, we can generate generate a model matrix which can be included in a Poisson point process model.

Quasi-random points are an alternative to grid-based or random background point designs. Quasi-random (sampling) background points are an advanced form of spatially-balanced survey design or point stratification, that aims to reduce the frequency of placing samples close to each other (relative to simple randomisations or grid designs). A quasi-random background point design improves efficiency of background point sampling (and subsequent modelling) by reducing the amount of spatial auto-correlation between data implying that each sample is providing as much unique information as possible (Grafston & Tille, 2013) and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007).

@@

Grafström, Anton, and Yves Tillé. "Doubly balanced spatial sampling with spreading and restitution of auxiliary totals." Environmetrics 24.2 (2013): 120-131.

>>>>

---
output:
  md_document:
    variant: gfm
---

@@

## qrbp is tempory R package that will be ingested into [ecomix](https://github.com/skiptoniam/ecomix) for generating quasi random background points for multiple species Poisson point process models.

The package aims to setup a model matrix for point process modelling for mulitple species (marked) point processes. The package is based on the quadrature scheme proposed by Berman & Turner 1993, and Warton & Shepard 2010. The idea bebind this package is simple, provided a set of presences for a species (or multiple species) and a spatial region, we can generate generate a model matrix which can be included in a Poisson point process model.  The code does provide the ability to produce a background point dataset without the inclusion of presences (a dummy grid) or for single species (which was developed as a proof of concept for the multispecies approach).

We also provide the capacity to generate quasi-random points are an alternative to grid-based or random background point designs. Quasi-random (sampling) background points are an advanced form of spatially-balanced survey design or point stratification, that aims to reduce the frequency of placing samples close to each other (relative to simple randomisations or grid designs). A quasi-random background point design improves efficiency of background point sampling (and subsequent modelling) by reducing the amount of spatial auto-correlation between data implying that each sample is providing as much unique information as possible (Grafston & Tille, 2013) and thus reducing low errors for geostatistical prediction (Diggle & Ribeiro, 2007).

For a worked example with single and multiple species presences see the package vignette.

@@

Grafstrom, Anton, and Yves Tille. "Doubly balanced spatial sampling with spreading and restitution of auxiliary totals." Environmetrics 24.2 (2013): 120-131.
